---
title: "Squid_prey_size"
author: "Elan Portner"
date: "4/29/2018"
output:
  html_document: default
  word_document: default
---

##Examining squid diet (new data from 2015, 2016, and 2017, and comparing to historical data from Unai)
####### Starting with summary of new data, collected by Portner 2015-2017

```{r, echo = FALSE,  warning=FALSE, message = FALSE}
### Load necessary packages ###
library(tidyverse)
library(tidyr)
library(ggplot2)
library(RColorBrewer)
library(colorRamps)
library(marmap)
library(ncdf4)
# library(ncdf) installation not working
library(RNetCDF)
library(raster)
library(maps)
library(mapdata)
library(maptools)
library(rgdal)
library(move)
library(mapproj)
library(sp)
require(dismo)
library(ggplot2)
library(ggmap)
library(RColorBrewer)
library(reshape2)
library(mapplots)
library(rgeos)
library(polyclip)
# library(spatstat) installation not working
library(Rmisc)

### Build color palettes ###
coul = brewer.pal(11, "RdBu")
coul = colorRampPalette(coul)(12)
coul2=colorRampPalette(coul)(20)
coul2 = c("#67001F", "#8E0C24" ,"#B01E2D", "#C5413E" ,"#D76654" ,"#E88B6E" ,"#F1AB8E" ,"#F9C8AF","#053061","#124984","#1F63A8","#2F79B5", "#3F8EC0","#61A6CD","#86BDDA", "#C5DEEC","#DBEAF2","#EDF2F5", "#66CDAA", "aquamarine4")
coul3=brewer.pal(11, "RdYlBu")
coul3=colorRampPalette(coul3)(22)
coul4=colorRampPalette(coul3)(16)

coul5 = brewer.pal(11, "Spectral")
coul5=colorRampPalette(coul5)(12)
coul6=colorRampPalette(coul5)(9)
### read specimen metadata ###
specimen <- read.csv("Dosidcus_specimens_2015-2017.csv")
specimen$year <- as.factor(specimen$year)
specimen$mat <- as.factor(specimen$mat)
specimen$fullness <- as.factor(specimen$fullness)

### read prey data. "squid" is all data, "prey" is PORTNER data only (2015, 2016 and 2017) ###
squid <- read.csv("Dosidicus_Diet_FINAL_Portner_only.csv")
squid$capture_lon <- ifelse(squid$capture_lon > 1, squid$capture_lon*-1, squid$capture_lon)
prey <- subset(squid, capture_year == "2015"|capture_year == "2016"|capture_year == "2017")
prey$fulltest <- prey$v_crustacean+prey$v_fish+prey$v_cephalopod+prey$v_other
I <- which(prey$fulltest == "0")
prey <- prey[-I,]
squidv <- prey[,c(1:18)]

### Preparing dataframe to examine changes in quantitative volume of prey groups ###
squidvl <- squidv %>% 
  gather(key   = Group,
         value = vgroup,
         dplyr::starts_with('v_'))
squidvl$vgroup <- squidvl$vgroup/100
squidvl$Group <- as.factor(squidvl$Group)
squidvl$capture_year <- as.factor(squidvl$capture_year)

squidvlsum <- aggregate(vgroup~Group*capture_year, squidvl, FUN = sum)
squidvlyear <- aggregate(vgroup~capture_year, squidvl, FUN = sum)
colnames(squidvlyear) <- c("capture_year", "yearN")

squidvlsum <- merge(squidvlsum, squidvlyear, by = "capture_year")
squidvlsum$prop <- squidvlsum$vgroup/squidvlsum$yearN

### Preparing dataframe to examine changes in percent number of prey groups for PORTNER and MARKAIDA diet data ###
squid$fulltest <- squid$v_crustacean+squid$v_fish+squid$v_cephalopod+squid$v_other
I <- which(squid$fulltest == "0")
squiddiet <- squid[-I,]

# REmove samples from very far North
I <- which(squiddiet$capture_lat>30)
squiddiet <- squiddiet[-I,]
# Remove samples from IMECOCAL
I <- which(squiddiet$capture_lat==25.5767)
squiddiet <- squiddiet[-I,]
# Remove samples from Volcan Marias
I <- which(squiddiet$capture_lon>(-108))
squiddiet <- squiddiet[-I,]
# Remove remaining samples fcollected in the Pacific
I <- which(squiddiet$locality=="OFF MAGDALENA")
squiddiet <- squiddiet[-I,]


squiddiet <- squiddiet[,c(1, 3:11,13, 19:40)]

squidl <- squiddiet %>% 
  gather(key   = Group,
         value = Nsquid,
         dplyr::starts_with('F_'),
         dplyr::starts_with('C_'),
         dplyr::starts_with('M_'),
         dplyr::starts_with('R_'))

squidl$capture_year <- as.factor(squidl$capture_year)

squidls <- aggregate(Nsquid~id, squidl, FUN = sum)
colnames(squidls) <- c("id", "totN")
squidlg <- merge(squidl, squidls, by = "id")
squidlg$PropN <- squidlg$Nsquid/squidlg$totN
squidlg$Group <- as.factor(squidlg$Group)

squidlsum <- aggregate(Nsquid~Group*capture_year, squidl, FUN = sum)
squidlyear <- aggregate(Nsquid~capture_year, squidl, FUN = sum)
colnames(squidlyear) <- c("capture_year", "yearN")

squidlsum <- merge(squidlsum, squidlyear, by = "capture_year")
squidlsum$prop <- squidlsum$Nsquid/squidlsum$yearN

#Preparing dataframe to examine changes in percent number of prey groups for PORTNER diet data only
prey <- prey[,c(1, 3:11,13, 19:40)]

preyl <- prey %>% 
  gather(key   = Group,
         value = Nprey,
         dplyr::starts_with('F_'),
         dplyr::starts_with('C_'),
         dplyr::starts_with('M_'),
         dplyr::starts_with('R_'))

preyl$capture_year <- as.factor(preyl$capture_year)

preyls <- aggregate(Nprey~id, preyl, FUN = sum)
colnames(preyls) <- c("id", "totN")
preylg <- merge(preyl, preyls, by = "id")
preylg$PropN <- preylg$Nprey/preylg$totN
preylg$Group <- as.factor(preylg$Group)

preylsum <- aggregate(Nprey~Group*capture_year, preyl, FUN = sum)
preylyear <- aggregate(Nprey~capture_year, preyl, FUN = sum)
colnames(preylyear) <- c("capture_year", "yearN")

preylsum <- merge(preylsum, preylyear, by = "capture_year")
preylsum$prop <- preylsum$Nprey/preylsum$yearN

#read prey size data
size <- read.csv("Dosidicus Prey Size 2018.csv")

I <- which(size$locality == "IMECOCAL"|size$locality == "VOLCAN MARIAS")
size <- size[-I,]
I <- which(size$year=="1995"|size$year=="2005"|is.na(size$year))
size <- size[-I,]

sizespec <- unique(size[,c(1,3,4,7:10)])

```


```{r, echo = FALSE,  warning=FALSE, message = FALSE}

### Summary figures of specimen size (ML), maturity, sex
histo1 <- ggplot(specimen, aes(x = ml, fill = year))+geom_histogram(colour = "black", binwidth = 2)
histo1 <- histo1 + xlab("Mantle Length (cm)")+ scale_fill_brewer(palette = "RdBu")+ggtitle("Fig. 1: Dosidicus collected from the GOC 2015 - 2017")+theme_dark()
histo1

histo1 <- ggplot(specimen, aes(x = ml, fill = year, color = year))+geom_density(binwidth = 1, alpha = 0.4)
histo1 <- histo1 + xlab("Mantle Length (cm)")+ scale_fill_brewer(palette = "RdBu")+ scale_color_brewer(palette = "RdBu")+ggtitle("Fig. 2: Dosidicus collected from the GOC 2015 - 2017")+theme_dark()
histo1

histo1 <- ggplot(specimen, aes(x = ml, fill = sex))+geom_histogram(colour = "black", binwidth = 2)+facet_wrap(~year)
histo1 <- histo1 + xlab("Mantle Length (cm)")+ scale_fill_brewer(palette = "RdBu")+ggtitle("Fig. 3: Sex of Dosidicus collected from the GOC 2015 - 2017")+theme_dark()
histo1

histo1 <- ggplot(specimen, aes(x = ml, fill = mat))+geom_histogram(colour = "black", binwidth = 2)+facet_wrap(~year)
histo1 <- histo1 + xlab("Mantle Length (cm)")+ scale_fill_brewer(palette = "RdBu")+ggtitle("Fig. 4: Maturity of Dosidicus collected from the GOC 2015 - 2017")+theme_dark()
histo1

histo1 <- ggplot(specimen, aes(x = ml, fill = fullness))+geom_histogram(colour = "black", binwidth = 2)+facet_wrap(~year)
histo1 <- histo1 + xlab("Mantle Length (cm)")+ scale_fill_brewer(palette = "RdBu")+ggtitle("Fig. 5: Fullness of Dosidicus collected from the GOC 2015 - 2017")+theme_dark()
histo1

```

####### Diet summary examining variation in qualitative percent volume of prey proups by year

```{r, echo = FALSE,  warning=FALSE, message = FALSE, fig.height=5, fig.width=7}
squidv$capture_year <- as.factor(squidv$capture_year)

# create map of GOC on which to plot sampling locations
baja <- getNOAA.bathy(lon1 = -108, lon2 = -113,
                        lat1 = 25, lat2 = 30, resolution = 1, keep=T)
blues <- c("lightsteelblue4", "lightsteelblue3",
           "lightsteelblue2", "lightsteelblue1")
# Plotting the bathymetry with different colors for land and sea
plot(baja, image = TRUE, land = TRUE, lwd = 0.1,
     bpal = list(c(0, max(baja), "grey"),
                 c(min(baja),0,blues)))
# Making the coastline more visible
plot(baja, deep = 0, shallow = 0, step = 0,
     lwd = 0.4, add = TRUE)
points(squidvl$capture_lon, squidvl$capture_lat, col = "black", pch = 21, bg = squidvl$capture_year)
legend("top",title="Year", legend=c("2015", "2016", "2017"), fill = c("black", "red", "green", pch = 19))
title(main = "Fig. 6: Map of distribution of D. gigas sampling locations in the GOC 2015-2017")
```

#### Diet summary examining variation in percent volume and percent number of prey species by year

```{r, echo = FALSE,  warning=FALSE, message = FALSE}

# comparing qualitative percent volume of prey groups between years
dietp <- ggplot(squidvlsum, aes(capture_year, prop, fill = Group))+geom_bar(stat="identity")+scale_fill_brewer(palette = "RdBu")+theme_dark()+theme(text=element_text(size=18))+xlab("Year")+ylab("Proportional Volume")+ggtitle("Fig. 7: Qualitative percent volume of prey groups by year")
dietp
```

###### Percent number. Crustaceans were recorded as presence absennce in PORTNER dataset (resulting in underestimation of importance)
```{r, echo = FALSE,  warning=FALSE, message = FALSE, fig.height=7, fig.width=10}

# comparing qualitative percent number of prey between years
preylsum$Group <- as.factor(preylsum$Group)
diet <- ggplot(preylsum, aes(capture_year, prop, fill = Group))+geom_bar(stat="identity")+scale_fill_manual(values=coul3)+theme_dark()+theme(text=element_text(size=18))+xlab("Year")+ylab("Numerical Proportion")+ggtitle("Fig. 8: Percent number of prey by year")
diet


```

##### To examine whether some of these differences are driven by spatial varitation in sampling coverage (2015 are all from Santa Rosalia, 2016 and 2017 were collected during cruises that sampled throughout the central GOC), I removed samples that were collected in 2016 and 2017 outside of waters adjacent to Santa Rosalia.
####### 2015: n = 100
####### 2016: n = 13
####### 2017: n = 8

```{r, echo = FALSE,  warning=FALSE, message = FALSE}

I <- which(squidvl$capture_lat>27.5|squidvl$capture_lat<27)
squidvl_mod <- squidvl[-I,]
I <- which(squidvl_mod$capture_lon>-111.75)
squidvl_mod <- squidvl_mod[-I,]

squidvl_modsum <- aggregate(vgroup~Group*capture_year, squidvl_mod, FUN = sum)
squidvl_modyear <- aggregate(vgroup~capture_year, squidvl_mod, FUN = sum)
colnames(squidvl_modyear) <- c("capture_year", "yearN")

squidvl_modsum <- merge(squidvl_modsum, squidvl_modyear, by = "capture_year")
squidvl_modsum$prop <- squidvl_modsum$vgroup/squidvl_modsum$yearN

baja2 <- getNOAA.bathy(lon1 = -111.75, lon2 = -112.5,
                        lat1 = 27.3, lat2 = 27.5, resolution = 1, keep=T)

# Plotting the bathymetry with different colors for land and sea
plot(baja2, image = TRUE, land = TRUE, lwd = 0.1, bpal = list(c(0, max(baja2), "grey"),
                 c(min(baja2),0,blues)))
# Making the coastline more visible
plot(baja2, deep = 0, shallow = 0, step = 0,
     lwd = 0.4, add = TRUE)
points(squidvl_mod$capture_lon, squidvl_mod$capture_lat, col = "black", pch = 21, bg = squidvl_mod$capture_year)
legend("left",title="Year", legend=c("2015", "2016", "2017"), fill = c("black", "red", "green", pch = 19))
title(main = "Fig. 9: Map of samples from immediate vicinity of Santa Rosalia 2015-2017")

dietp <- ggplot(squidvl_modsum, aes(capture_year, prop, fill = Group))+geom_bar(stat="identity")+scale_fill_brewer(palette = "RdBu")+theme_dark()+theme(text=element_text(size=18))+xlab("Year")+ylab("Proportional Volume")+ggtitle("Fig. 10: Proportional volume of prey groups in vicinity of Santa Rosalia 2015-2017")
dietp

I <- which(preyl$capture_lat>27.5|preyl$capture_lat<27)
preyl_mod <- preyl[-I,]
I <- which(preyl_mod$capture_lon>-111.75)
preyl_mod <- preyl_mod[-I,]

preyl_modsum <- aggregate(Nprey~Group*capture_year, preyl_mod, FUN = sum)
preyl_modyear <- aggregate(Nprey~capture_year, preyl_mod, FUN = sum)
colnames(preyl_modyear) <- c("capture_year", "yearN")

preyl_modsum <- merge(preyl_modsum, preyl_modyear, by = "capture_year")
preyl_modsum$prop <- preyl_modsum$Nprey/preyl_modsum$yearN

I <- which(preyl_modsum$Nprey==0)
preyl_modsum <- preyl_modsum[-I,]

diet <- ggplot(preyl_modsum, aes(capture_year, prop, fill = Group))+geom_bar(stat="identity")+scale_fill_manual(values=coul4)+theme_dark()+theme(text=element_text(size=18))+xlab("Year")+ylab("Numerical Proportion")+ggtitle("Fig. 11: Numerical percent composition of prey in vicinity of Santa Rosalia 2015-2017")
diet
```

#### Preliminary exploration of variability in _Dosidicus_ prey size during 1996-2017
###### specimens removed from dataset due to stomach preservaiton (1995-August 1996 in formaldehyde, degraded otoliths), collection outside of central GOC (IMECOCAL, Volcan Marias, Off Magdalena), or low sample sizes (n = 1 measured prey from 2005)
```{r, echo = FALSE,  warning=FALSE, message = FALSE}

# create map of GOC on which to plot sampling locations
baja3 <- getNOAA.bathy(lon1 = -108, lon2 = -114,
                        lat1 = 24, lat2 = 30, resolution = 1, keep=T)

# I <- which(is.na(size$length..cm.))
# size <- size[-I,1:18]
```

###### Size distribution of specimens
```{r summary plots, echo = FALSE, warning=FALSE, message = FALSE}
library(ggplot2)

sizespec$year <- as.factor(sizespec$year)
sizespecP <- subset(sizespec, year=="2015"|year=="2016"|year=="2017")

histo1 <- ggplot(sizespec, aes(x = ml, fill = year))+geom_histogram(colour = "black", binwidth = 2)
histo1 <- histo1 + xlab("Mantle Length (cm)")+ scale_fill_manual(values = coul)+ggtitle("Dosidicus collected from the GOC 1996 - 2017")+theme_dark()+theme(text=element_text(size=18))+xlab("Mantle Length (cm)")+ylab("Number of Stomachs")+ggtitle("Fig. 12: ML of squid for full D. gigas diet dataset")
histo1

squiddiet$capture_year <- as.factor(squiddiet$capture_year)

squidcol <- with(squiddiet, 
                 data.frame(capture_year = levels(capture_year),
                            color = coul5))
palette(coul5)
I <- which(squiddiet$capture_year == "2015"|squiddiet$capture_year == "2016"|squiddiet$capture_year == "2017")
squiddietunai <- squiddiet[-I,]
# Plotting the bathymetry with different colors for land and sea
plot(baja3, image = TRUE, land = TRUE, lwd = 0.1,
     bpal = list(c(0, max(baja3), "grey"),
                 c(min(baja3),0,blues)))
# Making the coastline more visible
plot(baja3, deep = 0, shallow = 0, step = 0,
     lwd = 0.4, add = TRUE)
points(squiddiet$capture_lon, squiddiet$capture_lat, pch = 21, col ="black", cex = 1, alpha = 0.3,
       bg = squiddiet$capture_year)
legend("topright",title="Year", legend=c("1996", "1997", "1998","1999","2005", "2006","2007", "2010", "2011","2015", "2016", "2017"), fill = c("#9E0142", "#D0384D" ,"#EE6445" ,"#FA9C58", "#FDCD7B" ,"#FEF0A7" ,"#F3FAAD", "#D0EC9C", "#98D5A4", "#5CB7A9", "#3682BA", "#5E4FA2"), pch = 19)
title(main="Fig. 13: Map of sampling locations of D. gigas in the GOC 1996-2017")

### As as frequency histogram ###
histo1 <- ggplot(sizespec, aes(x = ml, fill = year, color = year))+geom_density(binwidth = 1, alpha = 0.4)
histo1 <- histo1 + xlab("Mantle Length (cm)")+ scale_fill_manual(values = coul)+ scale_color_manual(values = coul)+ggtitle("Fig. 14: Dosidicus collected from the GOC 1996 - 2017")+theme_dark()
histo1

### Just for PORTNER data ###

# histo1 <- ggplot(sizespecP, aes(x = ml, fill = year))+geom_histogram(colour = "black", binwidth = 2)+facet_wrap(~year, nrow = 3)
# histo1 <- histo1 + xlab("Mantle Length (cm)")+ scale_fill_brewer(palette = "RdBu")+ggtitle("Dosidicus collected from the GOC 2015 - 2017 - Portner Dataset")+theme_dark()
# histo1

```

```{r, , echo = FALSE, warning=FALSE, message = FALSE, fig.height=7, fig.width=12}
# comparing qualitative percent number of prey between years
preylsum$Group <- as.factor(preylsum$Group)
diet <- ggplot(squidlsum, aes(capture_year, prop, fill = Group))+geom_bar(stat="identity")+scale_fill_manual(values=coul3)+theme_dark()+theme(text=element_text(size=18))+xlab("Year")+ylab("Numerical Proportion")+ggtitle("Fig. 15:Numerical percent composition of prey 1996-2017")
diet
```

## Relationship between ML and prey length
```{r, echo = FALSE,  warning=FALSE, message = FALSE}

size$author <- ifelse(size$year == "2015"|size$year == "2016"|size$year == "2017", "2015-2017", "1996-2011")
size$author <- as.factor(size$author)

size$year <- as.factor(size$year)

size$bin1 <- cut(size$ml, breaks = seq(10,85, by = 5), labels = c("10-15", "15-20", "20-25","25-30", "30-35","35-40", "40-45","45-50", "50-55","55-60", "60-65","65-70", "70-75","75-80", "80-85"))
size$season <- ifelse(size$month >5 & size$month <11, "summer", "winter")

fish <- subset(size, prey == "Benthosema"|prey=="Triphoturus")
ceph <- subset(size, prey == "Pterygioteuthis")

relat <- ggplot(ceph, aes(ml, DML, color = year))+geom_point()+geom_smooth(method = "lm")
relat <- relat + xlab("Mantle Length (cm)")+ylab("Pterygiotuethis ML (mm)")+ scale_color_manual(values = coul)+ggtitle("Fig. 16: Cephalopod prey size")+theme_dark()
relat
```

```{r,  warning=FALSE, message = FALSE}
anova.ceph <- aov(DML~year, ceph)
summary(anova.ceph)
TukeyHSD(anova.ceph)
```

```{r, echo = FALSE,  warning=FALSE, message = FALSE}
relat <- ggplot(fish, aes(ml, SL, color = year))+geom_point()+geom_smooth(method = "lm")+facet_wrap(~prey, nrow =2)
relat <- relat + xlab("Mantle Length (cm)")+ylab("Standard length (mm)")+ scale_color_manual(values = coul)+ggtitle("Fig. 17: Fish prey size")+theme_dark()
relat

```

```{r, warning=FALSE, message = FALSE}
bentho <- subset(fish, prey == "Benthosema")
tripho <- subset(fish, prey == "Triphoturus")
anova.fish <- aov(SL~year, bentho)
summary(anova.fish)
TukeyHSD(anova.fish)

anova.fish <- aov(SL~year, tripho)
summary(anova.fish)
TukeyHSD(anova.fish)
```


### Subsetting by summer months (June - October) to minimize variability driven by seasonality in prey size

```{r, echo = FALSE,  warning=FALSE, message = FALSE, fig.height=7, fig.width=12}
squiddiet$season <- ifelse(squiddiet$capture_month >5 & squiddiet$capture_month <11, "summer", "winter")
summer <- subset(squiddiet, season=="summer")
summer$capture_year <- as.factor(summer$capture_year)

I <- which(summer$capture_year=="1997"|summer$capture_year=="1998"|summer$capture_year=="1999")
summer <- summer[-I,]

plot(baja3, image = TRUE, land = TRUE, lwd = 0.1,
     bpal = list(c(0, max(baja3), "grey"),
                 c(min(baja3),0,blues)))
# Making the coastline more visible
plot(baja3, deep = 0, shallow = 0, step = 0,
     lwd = 0.4, add = TRUE)
points(summer$capture_lon, summer$capture_lat, pch = 21, col ="black", cex = 1, alpha = 0.3,
       bg = summer$capture_year)
legend("topright",title="Year", legend=c("1996", "2005", "2006","2007", "2010", "2011","2015", "2016", "2017"), fill = c("#9E0142", "#DB4849", "#F78E53", "#FDD180", "#F8F4AA", "#D4ED9E", "#89CDA5", "#4495B3" ,"#5E4FA2"), pch = 19)
title(main="Fig. 18: Map of sampling locations of D. gigas during summer in the GOC")

histo1 <- ggplot(summer, aes(x = mantle_length, group = capture_year, fill = capture_year))+geom_histogram(colour = "black", binwidth = 3)
histo1 <- histo1 + xlab("Mantle Length (cm)")+ scale_fill_brewer(palette = "RdBu")+ggtitle("Dosidicus collected GOC summer 1996 - 2017")+theme_dark()+theme(text=element_text(size=18))+xlab("Mantle Length (cm)")+ylab("Number of Stomachs")+ggtitle("Fig. 19: Size of specimens collected during summer in the GOC 1996-2017")
histo1

summerl <- summer %>% 
  gather(key   = Group,
         value = Nprey,
         dplyr::starts_with('F_'),
         dplyr::starts_with('C_'),
         dplyr::starts_with('M_'),
         dplyr::starts_with('R_'))

summerl$capture_year <- as.factor(summerl$capture_year)

summerls <- aggregate(Nprey~id, summerl, FUN = sum)
colnames(summerls) <- c("id", "totN")
summerlg <- merge(summerl, summerls, by = "id")
summerlg$PropN <- summerlg$Nprey/summerlg$totN
summerlg$Group <- as.factor(summerlg$Group)

summerlsum <- aggregate(Nprey~Group*capture_year, summerl, FUN = sum)
summerlyear <- aggregate(Nprey~capture_year, summerl, FUN = sum)
colnames(summerlyear) <- c("capture_year", "yearN")

summerlsum <- merge(summerlsum, summerlyear, by = "capture_year")
summerlsum$prop <- summerlsum$Nprey/summerlsum$yearN

summerl$Group <- as.factor(summerl$Group)

diet <- ggplot(summerlsum, aes(capture_year, prop, fill = Group))+geom_bar(stat="identity")+scale_fill_manual(values=coul3)+theme_dark()+theme(text=element_text(size=16))+xlab("Year")+ylab("Numerical Proportion")+ggtitle("Fig. 19: Numerical percent prey composition of squid collected during summer in the GOC 1996-2017")
diet
```


```{r, echo = FALSE,  warning=FALSE, message = FALSE}
size$year <- as.factor(size$year)
I <- which(size$month < 6 | size$month >10)
summersize <- size[-I,]
fish2 <- subset(summersize, prey == "Benthosema"|prey=="Triphoturus")
ceph2 <- subset(summersize, prey == "Pterygioteuthis")

relat <- ggplot(ceph2, aes(ml, DML, color = year))+geom_point()+geom_smooth(method = "lm")
relat <- relat + xlab("Mantle Length (cm)")+ylab("Pterygiotuethis ML (mm)")+ scale_color_brewer(palette = "RdBu")+gtitle("Fig. 20: Size of Pterygioteuthis from specimens collected during summer in the GOC 1996-2017")+theme_dark()+theme(text=element_text(size=18))
relat

anova.ceph <- aov(DML~year, ceph2)
summary(anova.ceph)
TukeyHSD(anova.ceph)
```

```{r, echo = FALSE,  warning=FALSE, message = FALSE, fig.height= 10, fig.width=12}
# relat1 <- ggplot(fish, aes(ml, SL, color = year, group = year))+geom_point()+geom_smooth(method = "lm")+facet_wrap(~prey, nrow = 2)
# relat1 <- relat1 + xlab("Mantle Length (cm)")+ylab("Standard Length (mm)")+ scale_color_brewer(palette = "RdBu")+ggtitle("Fish prey size")+theme_dark()
# relat1

relat1.2 <- ggplot(fish2, aes(ml, SL, color = year, group = year))+geom_point()+geom_smooth(method = "lm")+facet_wrap(~prey, nrow = 2)
relat1.2 <- relat1.2 + xlab("Mantle Length (cm)")+ylab("Standard Length (mm)")+ scale_color_brewer(palette = "RdBu")+gtitle("Fig. 21: Size of fish prey from specimens collected during summer in the GOC 1996-2017")+theme_dark()
relat1.2

benthosema2 <- subset(fish2, prey=="Benthosema")
anova.fish <- aov(SL~year, benthosema2)
summary(anova.fish)
TukeyHSD(anova.fish)

triphoturus2 <- subset(fish2, prey=="Triphoturus")
anova.fish <- aov(SL~year, triphoturus2)
summary(anova.fish)
TukeyHSD(anova.fish)
```

### Subsetting dataset for squid 20-25cm ML (highest overlap between new and historic diet datasets)

```{r, echo = FALSE,  warning=FALSE, message = FALSE}
small <- subset(size, ml <= 25 & ml >= 20 )
smallfish <- subset(small, prey == "Benthosema"|prey=="Triphoturus")
smallceph <- subset(small, prey == "Pterygioteuthis")

relat2 <- ggplot(smallceph, aes(ml, DML, color = year))+geom_point()
relat2 <- relat2 + xlab("Mantle Length (cm)")+ylab("Pterygiotuethis ML (mm)")+ scale_color_brewer(palette = "RdBu")+ggtitle("Cephalopod prey size in small squid (20-25cmML)")+theme_dark()
relat2

```

```{r, echo = FALSE,  warning=FALSE, message = FALSE, fig.height= 10, fig.width=12}
relat3 <- ggplot(smallfish, aes(ml, SL, color = year))+geom_point(size = 2)+facet_wrap(~prey, nrow = 2)
relat3 <- relat3 + xlab("Mantle Length (cm)")+ylab("Standard Length (mm)")+ scale_color_brewer(palette = "RdBu")+ggtitle("Fish prey size in small squid (20-25cmML)")+theme_dark()
relat3

```
<!-- ### Assigned specimens to length bins -->

<!-- ```{r, echo = FALSE,  warning=FALSE, message = FALSE, fig.height= 10, fig.width=12} -->

<!-- relat1 <- ggplot(fish, aes(bin1, SL, color = year))+geom_point()+facet_wrap(~prey, nrow = 2) -->
<!-- relat1 <- relat1 + xlab("Mantle Length (cm)")+ylab("Standard Length (mm)")+ scale_color_brewer(palette = "RdBu")+ggtitle("Fish prey size")+theme_dark() -->
<!-- relat1 -->

<!-- bentho <- subset(fish2, prey=="Benthosema") -->
<!-- bentho20 <- subset(bentho, bin1 == "20-25"|bin1 == "25-30") -->

<!-- size.aov <- aov(ml~year, bentho20) -->
<!-- summary(size.aov) -->
<!-- TukeyHSD(size.aov) -->


<!-- ``` -->

<!-- ```{r} -->
<!-- year.aov <- aov(SL~year, bentho20) -->
<!-- summary(year.aov) -->
<!-- TukeyHSD(year.aov) -->
<!-- ``` -->

```{r, echo = FALSE,  warning=FALSE, message = FALSE, fig.height=10}
relat4 <- ggplot(smallfish, aes(SL, group = author, fill = author))+geom_histogram(position = "identity", alpha = 0.5)+facet_wrap(~prey, nrow = 2, scales = "free_y")
relat4 <- relat4 + xlab("Standard Length (mm)")+scale_fill_manual(values = c("#AB1529","#1E61A5"))+ggtitle("Fish prey size in small squid (20-25cmML)")
relat4

relat5 <- ggplot(smallfish, aes(ml, group = author, fill = author))+geom_histogram(position = "identity", alpha = 0.5)+facet_wrap(~prey, nrow = 2, scales = "free_y")
relat5 <- relat5 + xlab("Mantle Length (cm)")+scale_fill_manual(values = c("#AB1529","#1E61A5"))+ggtitle("ML distribuiton of 'small' squid (20-25cmML)")
relat5

```

```{r, echo = FALSE,  warning=FALSE, message = FALSE}

testfish <- aov(ml~author*prey, smallfish)
testfish


t.test(ml~author, smallfish)

TukeyHSD(testfish)
# fishmeans <- aggregate(SL~year*prey, smallfish, FUN = mean)
# colnames(fishmeans) <- c("year","prey", "SL_mean")
# smallfish <-  merge(smallfish, fishmeans, by = "year"*"prey")
# boxes <- ggplot(smallfish, aes(year, SL_mean, fill = year))+geom_boxplot()+geom_point(aes(Year, SL_mean))+scale_fill_brewer(palette = "RdBu")
# boxes
```

